### 2018-12-16 tex/paper.tex
Higher-Potts model adjusted. There is some problem with the proof.

In this work, we establish a hitherto unknown connection between the submodular
extension of the Potts model proposed by Zhang et al.\citep{zhang2015higher}, and the
objective function of an accurate linear programming (LP) relaxation of the
corresponding MAP estimation problem~\citep{kleinberg2002approximation}. Specifically, the Lovasz extension of a submodular extension can be shown to be an objective function for the LP relaxation. This
connection has four important practical consequences. First, it establishes
the accuracy of the submodular extension of the Potts model, via the
UGC-hardness worst-case optimality of the LP relaxation. Second, it provides an
accurate submodular extension of the hierarchical Potts model, via the LP
relaxation of the corresponding MAP estimation problem proposed
by Kleinberg and Tardos \citep{kleinberg2002approximation}. Since any metric can be accurately
approximated as a mixture of hierarchical Potts
models~\citep{bartal1996probabilistic, bartal1998approximating}, this result
also provides a computationally feasible algorithm for estimating the marginals
for metric labeling. Third, it establishes the equivalence between the
subgradient of the LP relaxation and the conditional gradient of the problem of
minimising the upper bound of the log-partition. This allows us to employ the
widely used dense CRF, since the subgradient of its LP relaxation can be
efficiently computed using a recently proposed modified Gaussian filtering
algorithm~\citep{ajanthan2017efficient}. As a consequence, we provide the first
efficient algorithm to compute an upper bound of the log-partition function of
dense CRFs. This provides complementary information to the popular mean-field
inference algorithm for dense CRFs, which computes a lower bound on the
log-partition ~\citep{koltun2011efficient}. Fourthly, we obtain a good 
submodular extension for higher-order Potts model based on an accurate LP
relaxation. Higher-order Potts model is a generalisation of the pairwise Potts
model, and helps to capture interesting properties of the image that cannot be
done using pairwise models~\citep{vineet2014filter, kohli2009robust}. We show that our upper-bounds on synthetic problems are comparable to those from tree reweighted message passing (TRW)
~\citep{wainwright2005new} for the case of sparse CRFs. Unlike our approach,
TRW is computationally infeasible for dense CRFs, thereby limiting its use in
practice. Using pairwise dense CRF models, we perform stereo matching on standard
data sets and obtain better results than \citep{koltun2011efficient}. We also perform semantic segmentation on the MSRC-21 dataset

@@

\mysubsection{Pairwise Potts Model}
The pairwise Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. There are no higher-order potential terms in this model as in equation (\ref{eq:energy_min}).
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

@@

The simplest generalisation of pairwise Potts model to higher-order results in
\textit{higher-order Potts model}. The clique potentials for these models are
defined as

@@

\myparagraph{LP Relaxation}
\begin{align}
    \text{(HOP-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a = 1}^N
    \sum_{i = 1}^L \phi_a(i)y_{ai} + \nonumber\\
    &\sum_{c \in {\mathcal C}} \max_{(a, b) \in c} \frac{w_c}{2} \sum_{i = 1}^L \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:hop-lp}
\end{align}
The constraints for (HOP-LP) are the same as for (P-LP).

\myparagraph{LP-based Submodular Extension} We use the same $1-of-L$ encoding
scheme as for Potts model. In a similar way, problem can be rewritten as

@@

%Same as eq 5.6
\begin{align}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
\end{align}
where $f(.)$ is the Lovasz extension of $F(.)$. We are interested in making
this LP same as the (), thereby enabling us to recover the submodular extension
for higher-order Potts. The following proposition gives us the submodular
extension.
{\proposition The Lovasz extension of the following submodular extension for
  higher-order Potts model:
  \begin{align}
      F_{HOPotts}(A) &= \sum_a \sum_i \phi_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
        &\sum_{c \in {\mathcal C}} \max_{(a, b) \in c} \frac{w_c}{2} \sum_{i = 1}^L [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
is the objective function $E({\bf y})$ of the LP relaxation (HOP-LP).
\label{proposition:hop_extension}}
\begin{proof}
  We first observe that $\forall {\bf y} \in {\mathcal L}^N$, that is, for all
  valid labelings, $F_{HOPotts}(A_{\bf y})$ equals $E({\bf y}$.  Hence, $F_{HOPotts}$
    is an extension.

>>>>

In this work, we establish a hitherto unknown connection between the submodular
extension of the Potts model proposed by Zhang et al.\citep{zhang2015higher}, and the
objective function of an accurate linear programming (LP) relaxation of the
corresponding MAP estimation problem~\citep{kleinberg2002approximation}. Specifically, the Lovasz extension of a submodular extension can be shown to be an objective function for the LP relaxation. This
connection has four important practical consequences. First, it establishes
the accuracy of the submodular extension of the Potts model, via the
UGC-hardness worst-case optimality of the LP relaxation. Second, it provides an
accurate submodular extension of the hierarchical Potts model, via the LP
relaxation of the corresponding MAP estimation problem proposed
by Kleinberg and Tardos \citep{kleinberg2002approximation}. Since any metric can be accurately
approximated as a mixture of hierarchical Potts
models~\citep{bartal1996probabilistic, bartal1998approximating}, this result
also provides a computationally feasible algorithm for estimating the marginals
for metric labeling. Third, it establishes the equivalence between the
subgradient of the LP relaxation and the conditional gradient of the problem of
minimising the upper bound of the log-partition. This allows us to employ the
widely used dense CRF, since the subgradient of its LP relaxation can be
efficiently computed using a recently proposed modified Gaussian filtering
algorithm~\citep{ajanthan2017efficient}. As a consequence, we provide the first
efficient algorithm to compute an upper bound of the log-partition function of
dense CRFs. This provides complementary information to the popular mean-field
inference algorithm for dense CRFs, which computes a lower bound on the
log-partition ~\citep{koltun2011efficient}. Fourthly, we obtain a good 
submodular extension for higher-order Potts model based on an accurate LP
relaxation. Higher-order Potts model is a generalisation of the pairwise Potts
model, and helps to capture interesting properties of the image that cannot be
done using pairwise models~\citep{vineet2014filter, kohli2007p3}. We show that our upper-bounds on synthetic problems are comparable to those from tree reweighted message passing (TRW)
~\citep{wainwright2005new} for the case of sparse CRFs. Unlike our approach,
TRW is computationally infeasible for dense CRFs, thereby limiting its use in
practice. Using pairwise dense CRF models, we perform stereo matching on standard
data sets and obtain better results than \citep{koltun2011efficient}. We also perform semantic segmentation on the MSRC-21 dataset

@@

\mysubsection{Pairwise Potts Model}
The pairwise Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. There are no higher-order potential terms in this model as in equation (\ref{eq:energy_min}).
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}:
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

@@

One of the higher-order models used in practice is the \textit{higher-order Potts} model \citep{kappes2016higher}. For this model, the clique potentials $\phi_c({\bf x})$ in 
the energy function (equation (\ref{eq:energy_hop_min})) are defined as

@@

The higher-order Potts model differs from the $P^n$ Potts model \citep{kohli2007p3} in that the penalty for homogeneous labelings $\gamma_0$ is invariant to the label, that is, does not depend upon the label. We found this invariance property important in deriving the submodular extension from the LP relaxation.

\myparagraph{LP Relaxation}
We state the LP relaxation of the MAP estimation problem for higher-order Potts model. Let us assume the pairwise potentials in equation (\ref{eq:energy_hop_min}) to be Potts model. Also, we use the same set of indicator variables as for the Potts model. The following is an accurate LP relaxation for the higher-order Potts model:

\begin{align}
    \text{(HOP-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a = 1}^N
    \sum_{i = 1}^L \phi_a(i)y_{ai} + 
    \sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    & + \quad \sum_{c \in {\mathcal C}} \max_{(a, b) \in c} \frac{w_c}{2} \sum_{i = 1}^L \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:hop-lp}
\end{align}

The objective function is similar to that for the Potts model along with the addition of terms corresponding to higher-order potentials.The constraints for (HOP-LP) are the same as for (P-LP). To the best of our knowledge, the above LP relaxation does not have worst-case tightness guarantee, hence the submodular extension we derive using it does not have worst-case optimality property.

\myparagraph{LP-based Submodular Extension} We use the same $1-of-L$ encoding
scheme as for Potts model. Problem \ref{eq:min_upper_bound} then factorises as:

@@

%Same as eq 5.6
\begin{align}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
\end{align}
where $f(.)$ is the Lovasz extension of $F(.)$. We are interested in making
this LP same as the (), thereby enabling us to recover the submodular extension
for higher-order Potts. The following proposition gives us the submodular
extension.
{\proposition The Lovasz extension of the following submodular extension for
  higher-order Potts model:
  \begin{align}
      F_{HOPotts}(A) &= F_{Potts}(A) + \nonumber \\
        &\sum_{c \in {\mathcal C}} \max_{(a, b) \in c} \frac{w_c}{2} \sum_{i = 1}^L [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
is the objective function $E({\bf y})$ of the LP relaxation (HOP-LP).
\label{proposition:hop_extension}}
\newline
We note that the component of the submodular extension corresponding to cliques is of the form of maximum of cut function (that are submodular) over all pairs in a clique. In general, maximum of submodular functions is not submodular. However, in our particular case, the maximum turns out to be submodular as shown in the proof below.

\begin{proof}
  We first observe that $\forall {\bf y} \in {\mathcal L}^N$, that is, for all
  valid labelings, $F_{HOPotts}(A_{\bf y})$ equals $E({\bf y}$.  Hence, $F_{HOPotts}$
    is an extension.
